sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-26 doc/paper.Rmd
Remove 3rd pcod eg

As a third example, we could model presence/absence of Pacific cod (`present`) with a time-varying quadratic effect of depth, an independent mean each year, a spatial random field, and IID spatiotemporal fields:

@@

```{r, eval=FALSE, echo=TRUE}
fit_spatiotemporal_tv <- sdmTMB(
  present ~ 0 + as.factor(year), 
  time_varying = ~ 0 + poly(depth, 2), 
  family = binomial(), data = pcod, mesh = mesh,
  time = "year", spatial = "on", spatiotemporal = "iid"
)
```

>>>>

<!-- As a third example, we could model presence/absence of Pacific cod (`present`) with a time-varying quadratic effect of depth, an independent mean each year, a spatial random field, and IID spatiotemporal fields: -->

@@

```{r, eval=FALSE, echo=FALSE}
fit_spatiotemporal_tv <- sdmTMB(
  present ~ 0 + as.factor(year), 
  time_varying = ~ 0 + poly(depth, 2), 
  family = binomial(), data = pcod, mesh = mesh,
  time = "year", spatial = "on", spatiotemporal = "iid"
)
```
